Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-07 analysis/paper/paper.Rmd
Put supplementary materials in paper document
Try to get them to knit in the Docker this way

>>>>

# Supplementary Materials

## Tables

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f1_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of journal title on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f2_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of journal title on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g1_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  mutate(Parameter = gsub("year", "", .$Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of year of publication on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g2_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  mutate(Parameter = gsub("year", "", .$Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of year of publication on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h1_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of five-year impact factor on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h2_report) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of five year impact factor on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

## Figures

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:22, 1:20)]

p <- plot(equivalence_test(m_f1)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
))
```

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability.."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]

p <- plot(equivalence_test(m_f2)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
))
```

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(10:11, 1:9)]

p <- plot(equivalence_test(m_g1)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
))
```

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_g2)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
))
```

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
p <- plot(equivalence_test(m_h1))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
))
```

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_h2))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
))
```
